---
title: "Tools and Techniques"
author: "Kyle Deisher"
date: "10/30/21"
output:
  pdf_document:
    keep_tex: yes
    latex_engine: xelatex
  html_document: default
graphics: yes
---

#First I will demonstrate what a multivariate bubble plot looks like and how one is created.




#One multivariate plot that is very specific and used in our project is the United States plot which I will demonstrate how to create and modify below


#Line plots are used to show how variables change over time adn these plots can also display multiple variables as well

```{r}
library(ggplot2)
library(tidyverse)
library(gganimate)
library(ggthemes)
library(babynames)
```


#Sections of this graph can still be confusing to interpret like the male babies for perdominately female names and vice versa but can be understood better when adding some animation.

```{r}
library(gifski)
library(transformr)
Data_3 <- Data_2[1:150,]
plot <- ggplot(data = Data_2, aes(x=year, y=n, color=sex,linetype=name)) + geom_line(size=1.2)+ xlab("Year") + ylab("Number of Babies") + ggtitle("Number of Babieswith the names Ashley, Adam, or Helen") + theme(axis.text.x = element_text(size=16), axis.title.x = element_text(size=18), axis.text.y = element_text(size=16), axis.title.y = element_text(size=18), legend.text = element_text(size=16), legend.key.size = unit(1,'cm'), legend.title = element_text(size=16), plot.title = element_text(size=14))
plot
#animate(plot, renderer = gifski_renderer(), duration =20)
```








#Changing the variables of color and name allow you to show the needed variables in different ways

```{r}
Data_3 <- Data_2[1:150,]
plot <- ggplot(data = Data_2, aes(x=year, y=n, color=name,linetype=sex)) + geom_line(size=1.2)+ xlab("Year") + ylab("Number of Babies") + ggtitle("Number of Babies with the names Ashley, Adam, or Helen") + theme(axis.text.x = element_text(size=16), axis.title.x = element_text(size=18), axis.text.y = element_text(size=16), axis.title.y = element_text(size=18), legend.text = element_text(size=16), legend.key.size = unit(1,'cm'), legend.title = element_text(size=16), plot.title = element_text(size=14))
plot
#animate(plot, renderer = gifski_renderer(), duration =20)
```




















#Downsides of multivariate line graphs Also I increase the FPS to 24 since the default is 10 which can look slightly choppy but had to speed up the duration due to rendering time
```{r}
Data_4<- babynames %>% filter(name %in% c("Ashley", "Adam", "Helen", "Ethan", "Tom", "John", "Michelle", "Jane"))
plot4 <- ggplot(data = Data_4, aes(x=year, y=n, color=name,linetype=sex)) + geom_line(size=1.2) + transition_reveal(year)+ xlab("Year") + ylab("Number of Babies") + ggtitle("Number of Babies over the years") + theme(axis.text.x = element_text(size=16), axis.title.x = element_text(size=18), axis.text.y = element_text(size=16), axis.title.y = element_text(size=18), legend.text = element_text(size=16), legend.key.size = unit(1,'cm'), legend.title = element_text(size=16), plot.title = element_text(size=14))
animate(plot4, renderer = gifski_renderer(), duration =20)
```





















```{r}
Data_4<- babynames %>% filter(name %in% c("Ashley", "Adam", "Helen", "Ethan", "Tom", "John", "Michelle", "Jane"))
plot4 <- ggplot(data = Data_4, aes(x=year, y=n, color=name,linetype=sex)) + geom_line(size=1.2) + transition_reveal(year)+ xlab("Year") + ylab("Number of Babies") + ggtitle("Number of Babies over the years") + theme(axis.text.x = element_text(size=16), axis.title.x = element_text(size=18), axis.text.y = element_text(size=16), axis.title.y = element_text(size=18), legend.text = element_text(size=16), legend.key.size = unit(1,'cm'), legend.title = element_text(size=16), plot.title = element_text(size=14))
animate(plot4, renderer = gifski_renderer(), duration =5, fps=24)
```